%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}
\usepackage{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Mathew Syriac Madhavacheril}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{\\Department of Astrophysical Sciences\\Princeton University\\Princeton, NJ 08544\\}
\address{\\Email: mathewm@astro.princeton.edu\\Web: msyriac.github.io\\Tel: +1 631 682 1681}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{Education}
\textbf{Stony Brook University}, Stony Brook, NY\\
{\sl PhD} (2016), {\sl MA} (2013) Physics
\\ \\
\textbf{University of Cambridge}, Cambridge, UK\\
{\sl MA, BA Affiliated}, Part II and Part III Natural Sciences (Physics), First Class, 2011\hfill 
\\ \\
\textbf{St. Stephen's College, University of Delhi}, New Delhi, India\\
{\sl BSc. (Hons.)}, Physics, First Class, 2009\hfill 

\section{Research \\Interests}
Cosmology and particle astrophysics; data analysis and theory \\
CMB lensing; optical weak lensing and shear estimation; joint CMB/optical probes \\
Galaxy clusters; growth of structure \\
Astrophysical probes of particle dark matter

\section{Academic Appointments}
\textbf{Postdoctoral Research Associate (2016-)}\\
Department of Astrophysical Sciences, Princeton University, Princeton NJ
\\

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{Awards and Grants}
\par
%\textbf{Project One}: 
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Pellentesque semper 
%vulputate vestibulum. Pellentesque viverra orci vitae dolor ultrices, eu semper 
%ex blandit. 
\begin{itemize}
\item Astronomical Society of New York (ASNY) Graduate Student Paper Prize (2015)
\item LSST-DESC Student Travel Grant (2015)
\item {\sl Editor's Suggestion} and {\sl Viewpoint in Physics} pick for first-author paper in {\sl Physical Review Letters} (2015)
\item H. B. Silsbee Award for Excellence, Physics Department, Stony Brook University (2015)
\item Jonathan Kauffman Student Excellence Prize in Physics, Physics Department, Stony Brook University (2014)
\item Jennings Prize, Wolfson College, University of Cambridge (2011)
\item Gates Cambridge Scholarship, University of Cambridge (2009) %\footnote{\url{https://www.gatescambridge.org/about}}
\end{itemize}

\section{Teaching Experience}
\begin{itemize}
\item Adviser for undergraduate researcher Teva Ilan at Princeton University (2017)
\item Co-adviser for undergraduate researchers Ho Nam Nguyen and Danylo Yakymiv at Stony Brook University (2016)
\item Teaching Assistant, Stony Brook University (2011 - 2013)
\item Faculty, Cambridge Tradition and Cambridge Prep Summer Schools, Oxbridge Academic Programs, UK (2011, 2012)
\end{itemize}

\section{Professional Service}
\begin{itemize}
\item Referee for {\sl Nature Astronomy} and {\sl Monthly Notices of the Royal Astronomical Society}
\item Remote Observing Coordinator (ROC) for ACTPol observations since 09/14
\item Visited the ACTPol telescope site on Cerro Toco, Chile, 12/13 to help with site operations
\end{itemize}

\section{Collaborations}
\begin{itemize}
\item Atacama Cosmology Telescope (ACT) (involved with ACTPol and Advanced ACT analysis)
\item Simons Observatory - lensing and SZ working groups
\item Hyper Suprime-Cam (HSC) survey
\item CMB Stage IV - lensing and dark energy working groups
\item LSST Dark Energy Science Collaboration (DESC)
\end{itemize}

\section{Talks}

\begin{itemize}
\item Seminar at Rutgers University, New Brunswick NJ 11/17
\item DPF2017 Conference, Fermilab 08/17
\item WIN2017 Conference, Irvine CA, 06/17
\item Seminar at University of Pennsylvania, Philadelphia PA 02/17
\item Gravity Group Seminar, Princeton University, NJ 12/16
\item Seminar at Perimeter Institute for Theoretical Physics, Waterloo, Canada 11/16
\item APEC Seminar at Kavli IPMU, Kashiwa, Japan, 04/16
\item Contributed Talk at {\sl Future Challenges in Shear Estimation}, University of Pennsylvania, PA 11/15
\item Astrophysics Seminar, Imperial College, UK 09/15
\item Astrophysics Seminar, University College London, UK 09/15
\item Institute of Astronomy Seminar, University of Cambridge, UK 09/15
\item Oxford Astrophysics Seminar, University of Oxford, UK 09/15
\item Contributed Talk at {\sl Cosmology Meeting 2015}, Barcelona 09/15
\item Joint Stony Brook / Brookhaven National Lab Cosmology Seminar, NY 06/15
\item Seminar at Canadian Institute for Theoretical Astrophysics, Toronto 05/15
\item Seminar at Perimeter Institute for Theoretical Physics, Waterloo, Canada 05/15
\item Yang Institute for Theoretical Physics Seminar, Stony Brook, NY 02/15
\item Department of Astronomy Seminar, Columbia University, NY 02/15
\item Cosmology Lunch Seminar, Princeton University, NJ 01/15
\item Department of Physics \& Astrophysics Seminar, University of Delhi, India 08/14
\end{itemize}

\section{Publications}

\textbf{First or Second Author}
\\
\begin{enumerate}
 \item ``The weight of cosmic lenses'', {\bf M. S. Madhavacheril}, invited {\sl News and Views} article for  {\sl Nature Astronomy}, 2017
\item ``Fundamental Physics from Future Weak-Lensing Calibrated Sunyaev-Zel'dovich Galaxy Cluster Counts'', {\bf M. S. Madhavacheril}, N. Battaglia, H. Miyatake, {\sl Physical Review D}, 2017
\item ``Internal Delensing of Cosmic Microwave Background Acoustic Peaks'', N. Sehgal, {\bf M. S. Madhavacheril}, B. Sherwin, A. van Engelen, {\sl Physical Review D}, 2017
\item ``Measurement of a Cosmographic Distance Ratio with Galaxy and CMB Lensing'', H. Miyatake, {\bf M. S. Madhavacheril}, N. Sehgal, A. Slosar, D. N. Spergel, B. Sherwin, A. van Engelen, {\sl Physical Review Letters}, 2016
\item ``Evidence of Lensing of the Cosmic Microwave Background by Dark Matter Halos'', {\bf M. S. Madhavacheril}, N. Sehgal et. al. (ACTPol Collaboration), {\sl Physical Review Letters}, 2015, picked as {\sl Editor's Suggestion} and selected for {\sl Viewpoint in Physics}
\item ``Building unbiased estimators from non-Gaussian likelihoods with application to shear estimation'', {\bf M. S. Madhavacheril}, P. McDonald, N. Sehgal, A. Slosar, {\sl Journal of Cosmology and Astroparticle Physics}, 2015
\item ``Current dark matter annihilation constraints from CMB and low-redshift data'', {\bf M. S. Madhavacheril}, N. Sehgal, T. R. Slatyer, {\sl Physical Review D}, 2014
\end{enumerate}
%\newpage
\textbf{Major contributions}
\\
\begin{enumerate}
\setcounter{enumi}{7}
\item ``Measuring the Small-Scale Matter Power Spectrum with High-Resolution CMB Lensing'', H. N. Nguyen, N. Sehgal, {\bf M. S. Madhavacheril}, arXiv:1710.03747, submitted to {\sl Physical Review D}, 2017
\item ``MassiveNuS: Cosmological Massive Neutrino Simulations'', J. Liu, S. Bird, J. Matilla, J. C. Hill, Z. Haiman, {\bf M. S. Madhavacheril}, A. Petri, D. N. Spergel, arXiv:1711.10524, submitted to {\sl Journal of Cosmology and Astroparticle Physics}, 2017
\item ``The Atacama Cosmology Telescope: Two-Season ACTPol Lensing Power Spectrum'', B. Sherwin, A. van Engelen, N. Sehgal, {\bf M. S. Madhavacheril} et. al. (ACTPol Collaboration), {\sl Physical Review D}, 2016
\end{enumerate}
\textbf{Minor contributions}
\\
\begin{enumerate}
\setcounter{enumi}{10}
\item ``Non-Gaussianity of secondary anisotropies from ACTPol and Planck'', W. Coulton et. al. (incl. {\bf M. S. Madhavacheril}), arXiv:1711.07879, submitted to {\sl Journal of Cosmology and Astroparticle Physics}, 2017
\item ``The Atacama Cosmology Telescope: The Two-Season ACTPol Sunyaev-Zeldovich Effect Selected Cluster Catalog'', M. Hilton, M. Hasselfield, C. Sifón, N. Battaglia et. al. (incl. {\bf M. S. Madhavacheril}), accepted for publication in {\sl Astrophysical Journal Supplement}, 2017
\item ``CMB-S4 Science Book'', Abazajian et. al. (incl. {\bf M. S. Madhavacheril}), 2016
\item ``The Atacama Cosmology Telescope: Two-Season ACTPol Spectra and Parameters'', T. Louis, E. Grace, M. Hasselfield, M. Lungu, L.  Maurin et. al. (incl. {\bf M. S. Madhavacheril}), 2016
\item ``Survey strategy optimization for the Atacama Cosmology Telescope'', F De Bernardis, JR Stevens, M Hasselfield et. al. (incl. {\bf M. S. Madhavacheril}), {\sl SPIE Astronomical Telescopes+ Instrumentation}, 2016
\item ``Detection of the pairwise kinematic Sunyaev-Zel'dovich effect with BOSS DR11 and the Atacama Cosmology Telescope'', F De Bernardis, S Aiola, EM Vavagiakis, MD Niemack et. al. (incl. {\bf M. S. Madhavacheril}), 2016
\item ``Evidence for the kinematic Sunyaev-Zel’dovich effect with the Atacama Cosmology Telescope and velocity reconstruction from the Baryon Oscillation Spectroscopic Survey'', E. Schaan, S. Ferraro, M. Vargas-Magaña, K. M. Smith, S. Ho et. al. (incl. {\bf M. S. Madhavacheril}), {\sl Physical Review D}, 2016
\item ``The Atacama Cosmology Telescope: measuring radio galaxy bias through cross-correlation with lensing'', R. Allison, S. N. Lindsay, B. D. Sherwin et. al. (incl. {\bf M. S. Madhavacheril}), {\sl Monthly Notices of the Royal Astronomical Society}, 2015
\item ``The Atacama cosmology telescope: Lensing of CMB temperature and polarization derived from cosmic infrared background cross-correlation'', A. van Engelen, B. D. Sherwin, N. Sehgal et. al. (incl. {\bf M. S. Madhavacheril}), {\sl The Astrophysical Journal}, 2014
\item ``The Atacama Cosmology Telescope: CMB Polarization at $200< \ell< 9000$'', S. Naess, M. Hasselfield, J. McMahon, M. D. Niemack et. al. (incl. {\bf M. S. Madhavacheril}), {\sl Journal of Cosmology and Astroparticle Physics}, 2014
\end{enumerate}

\end{resume}
\end{document}
